Sorting algorithms: how are they affected by memory faults?

### 2019-12-18 paper/MaterialsAndMethods.tex
adicao de imagens e continuacao da escrita

To be continued...

@@

Based on the output files generated before, we produce the ...

>>>>

\textcolor{red}{To be continued...}

@@

Based on the output files generated before, our starting point was to test if the dataset had a normal distribution. To achieve this, we use Shapiro-Wilk normality test. After we run these tests, only the distribution related to the dependent variable \textit{unordered elements size} was considered normal. Figure \ref{fig-distribution-graph} shows an example of this distribution. In these graphs, the red vertical line means the mean, and the blue vertical line means the median. The distributions were normal in all combinations of independent variables for dependent variable \textit{unordered elements size}.

\begin{figure}[H]
    \centering
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Bubble_distribution_graph}}
     \textsf{\caption[Distribution Graph for bubblesort.]{Distribution Graph for bubblesort.\label{fig-dist-bubble-001-100}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Insertion_distribution_graph.png}}
     \textsf{\caption[Distribution Graph for insertion sort.]{Distribution Graph for insertion sort.\label{fig-dist-insertion-001-100}}}
     \end{subfigure}
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Merge_distribution_graph.png}}
     \textsf{\caption[Distribution Graph for mergesort.]{Distribution Graph for mergesort.\label{fig-dist-merge-001-100}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Quick_distribution_graph.png}}
     \textsf{\caption[Distribution Graph for quicksort.]{Distribution Graph for quicksort.\label{fig-dist-quick-001-100}}}
     \end{subfigure}
     \caption{Distribution graph for a probability failure of 1\% and a sequence size of 10000.}
    \label{fig-distribution-graph}
\end{figure}

Q-Q plot shows that how much more blue points close to the red line, most normal is the distribution. Figure \ref{fig-qqplot} below presents this graph for a probability failure of 1\% and a sequence size of 10000 for considered sorting algorithms.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.37]{figures/anova_prob_0_01_tam_10000_DESORDENADOS_PERCENTUAL.png}
    \textsf{\caption[Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.]{Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.\label{fig-qqplot}}}
 \end{figure}
